Exploring Disparate Data: Part 1

### 2024-11-01 A3-Pt1.Rmd
Update A3-Pt1.Rmd
at_cyclone All tests passed!

- 
- 
- 
- 
-

@@

# Same steps as in A2, but you can put them all in the same pipeline!
at_cyclone <- str_c(cyclone_data_address, at_cyclone_filename, sep = "") |>
    read_csv(
        col_names = c(as.character(1:4)),
        progress = FALSE,
        show_col_types = FALSE
    ) |>
    separate_wider_delim(
        cols = `4`,
        # Set the delim and the names
        # YOUR CODE HERE
    ) |>
    mutate(
        across(everything(), str_trim),
        # make "-999" NAs, make "-99" NAs
        # Create columns BasinNumberYear, Name, and Entries
        across(everything(), ~na_if(., "-999")),
        across(everything(), ~na_if(., "-99")),
        BasinNumberYear = ifelse(is.na(status), `1`, NA),
        Name = ifelse(is.na(status), `2`, NA),
        Entries = ifelse(is.na(status), `3`, NA)
    ) |>
    relocate(BasinNumberYear, Name, Entries) |>
    fill(BasinNumberYear, Name, Entries) |>
    filter(!is.na(status))  |>
    select(-Entries) |>
    separate_wider_position(
        BasinNumberYear,
        # Specify the widths
        # YOUR CODE HERE
    ) |>
    separate_wider_position(
        `1`,
        # Specify the widths
        # YOUR CODE HERE
    ) |>
    separate_wider_position(
        `2`,
        # Specify the widths
        # YOUR CODE HERE
    ) |>
    rename(
        Identifier = `3`
    ) |>
    mutate(
        across(
            c(NameYear, ObservYear, Month, Day, Hour,
                Minute, Number),
            as.integer
        )
    ) |>
    mutate(across(max_wind:r_max_wind, as.numeric))

@@

Write a function that takes in a vector of latitude _or_ longitude in the format of these data, then outputs a positive version of the numeric part if there's an "N" or an "E", and a negative version of the numeric part if there's a "W" or "S".

@@

Categorize the cyclones based on the scale above using a `case_when()` statement based on the `max_wind` column. The code is set up to create an [*ordered factor*](https://fralfaro.github.io/r4ds/factors.html) so that R knows that the levels are ordered as TD < TS < 1 < 2 < 3 < 4 < 5.
```{r cyclones_data}
cat_levels <- c("TD", "TS", "1", "2", "3", "4", "5")

@@

Now that we have a suitable data frame, save it as a parquet file with the file name `"cyclones_data.parquet"`.
```{r}
# YOUR CODE HERE
```

@@

| year  | region    | name | value   |
|-------|-----------|------|---------|
| 1978  | Antarctic | min  | 7.283   |
| 1978  | Antarctic | max  | 17.803  |
| 1978  | Arctic    | min  | 10.231  |
| 1978  | Arctic    | max  | 14.585  |
| 1979  | Antarctic | min  | 2.911   |
| 1979  | Antarctic | max  | 18.361  |
| ...   | ...       | ...  | ...     |

@@

- "Bolivia (Plurinational State of)", "Congo (Democratic Republic of the)", "Egypt", "Hong Kong", "Lao People's Democratic Republic", "Slovakia", "North MAcedonia", "South Korea" (be careful with this one!), "Turkey", "Vietnam", "Yemen".
```{r aware_fixed_country_match}
aware_fixed_country_match <- aware_fixed_country |>
    mutate(
        # Change country using a case_when statement
        # YOUR CODE HERE
    )

@@

happiness
```
```{r}
. = ottr::check("tests/happiness.R")
```

>>>>

-   Aditya
-   Andy
-   Dibu
-   Oscar
-   Taras

@@

# Same steps as in A2, but you can put them all in the same pipeline!
at_cyclone <- str_c(cyclone_data_address, at_cyclone_filename, sep = "") |>
    read_csv(
        col_names = c(as.character(1:4)),
        progress = FALSE,
        show_col_types = FALSE
    ) |>
    filter(!grepl("AL", `4`)) |>
    separate_wider_delim(
        cols = `4`,
        # Set the delim and the names
        # YOUR CODE HERE
    ) |>
    mutate(
        across(everything(), str_trim),
        # make "-999" NAs, make "-99" NAs
        # Create columns BasinNumberYear, Name, and Entries
        across(everything(), ~na_if(., "-999")),
        across(everything(), ~na_if(., "-99")),
        BasinNumberYear = ifelse(is.na(status), `1`, NA),
        Name = ifelse(is.na(status), `2`, NA),
        Entries = ifelse(is.na(status), `3`, NA)
    ) |>
    relocate(BasinNumberYear, Name, Entries) |>
    fill(BasinNumberYear, Name, Entries) |>
    filter(!is.na(status))  |>
    select(-Entries) |>
    separate_wider_position(
        BasinNumberYear,
        # Specify the widths
        # YOUR CODE HERE
    ) |>
    separate_wider_position(
        `1`,
        # Specify the widths
        # YOUR CODE HERE
    ) |>
    separate_wider_position(
        `2`,
        # Specify the widths
        # YOUR CODE HERE
    ) |>
    rename(
        Identifier = `3`
    ) |>
    mutate(
        across(
            c(NameYear, ObservYear, Month, Day, Hour,
                Minute, Number),
            as.integer
        )
    ) |>
    mutate(across(max_wind:r_max_wind, as.numeric))

@@

Write a function that takes in a vector of latitude *or* longitude in the format of these data, then outputs a positive version of the numeric part if there's an "N" or an "E", and a negative version of the numeric part if there's a "W" or "S".

@@

Categorize the cyclones based on the scale above using a `case_when()` statement based on the `max_wind` column. The code is set up to create an [*ordered factor*](https://fralfaro.github.io/r4ds/factors.html) so that R knows that the levels are ordered as TD \< TS \< 1 \< 2 \< 3 \< 4 \< 5.

```{r cyclones_data}
cat_levels <- c("TD", "TS", "1", "2", "3", "4", "5")

@@

Now that we have a suitable data frame, save it as a parquet file with the file name `"cyclones_data.parquet"`.

```{r}
# YOUR CODE HERE
```

@@

| year | region    | name | value  |
|------|-----------|------|--------|
| 1978 | Antarctic | min  | 7.283  |
| 1978 | Antarctic | max  | 17.803 |
| 1978 | Arctic    | min  | 10.231 |
| 1978 | Arctic    | max  | 14.585 |
| 1979 | Antarctic | min  | 2.911  |
| 1979 | Antarctic | max  | 18.361 |
| ...  | ...       | ...  | ...    |

@@

-   "Bolivia (Plurinational State of)", "Congo (Democratic Republic of the)", "Egypt", "Hong Kong", "Lao People's Democratic Republic", "Slovakia", "North MAcedonia", "South Korea" (be careful with this one!), "Turkey", "Vietnam", "Yemen".

```{r aware_fixed_country_match}
aware_fixed_country_match <- aware_fixed_country |>
    mutate(
        # Change country using a case_when statement
        # YOUR CODE HERE
    )

@@

happiness
```

```{r}
. = ottr::check("tests/happiness.R")
```
